
\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx, pgfplots,xfrac} 
\usepackage[all]{xy}
\usepackage{polynom} 
%\usepackage{pdfsync} %% I don't know why this messes up tabular column widths
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}

\pgfplotsset{compat=1.6}

\pgfplotsset{soldot/.style={color=black,only marks,mark=*}} \pgfplotsset{holdot/.style={color=black,fill=white,only marks,mark=*}}

\usetikzlibrary{calc}
\tikzstyle{vertex}=[circle, draw, fill=black, inner sep=1pt, minimum size=6pt]


\pagestyle{fancy} 
\lfoot{}
\rfoot{3-9 \& 4-1 prep}

\begin{document}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\renewcommand{\d}{\displaystyle}

\vspace*{-0.7in}

%%%%%%%%%intro page
\begin{center}
  \large
  \sc{Recitation: Week 7}\\ 
\end{center}
 This work sheet has three parts:
 \begin{itemize}
 \item a mini-practice derivative proficiency
 \item prep for 3.9 homework
 \item prep for 4.1 homework
 \end{itemize}
  \begin{center} Mini-Derivative Proficiency \end{center}
You have 15 minutes to write the derivatives of the six functions (three on this page and three on the next). You do not need to simplify. You do need to identify that you are taking the derivative (i.e. write $y'$ or $f'(x)$ or whatever is proper notation.)

 \begin{enumerate}
 \item \large{$g(x)=4x^{\pi}-e^2$}
 \vfill
 \item  \large{$f(\theta)=\theta \tan (2 \theta)$}
 \vfill
 \item  \large{$\displaystyle{y=\frac{-3}{\sqrt{4-x^2}}}$}
 \vfill
 \newpage
 \item \large{$f(x)=\frac{\tan^{-1}(5x)}{10}$} 
 \vfill
 \item  \large{$y=2x+\sqrt{3x+\sin(4x)}$}
 \vfill
 \item Find $dy/dx$ for \large{$x^3 y^3=x+y$ }
 \vfill
 \end{enumerate}
 \newpage
 
 \begin{center} 3.9 Homework Help \end{center}
 
 \begin{enumerate}
 \item Complete the derivative formulas below:
 \begin{multicols}{2}
 \begin{enumerate}
 	\item $\displaystyle{\frac{d}{dx} \left[e^x \right]=}$
	\item $\displaystyle{\frac{d}{dx} \left[10^x \right]=}$
	\item $\displaystyle{\frac{d}{dx} \left[\ln(x) \right]=}$
	\item $\displaystyle{\frac{d}{dx} \left[\log_{10}(x) \right]=}$
\end{enumerate}
\end{multicols}
\item Complete the algebraic rules below:
 \begin{multicols}{2}
 \begin{enumerate}
 	\item $\displaystyle{e^{a+b}=}$
	\item $\displaystyle{\ln(ab)=}$
	\item $\displaystyle{\ln(a^r)=}$
\end{enumerate}
\end{multicols}
\item Find the derivative of $f(x)=e^{5x+2}$ in two ways: (a) without rewriting the function and (b) rewriting the function using the rule on exponents above.
\vfill
\item Find the derivative of $f(x)=\ln(5x^3)$ in two ways: (a) without rewriting the function and (b) rewriting the function using the rule on logarithms above. Show that your answers are the same.
\vfill
\item For each expression below, take the logarithm of both sides. Then use rules of logarithms to expand the right-hand side of the expression.
\begin{enumerate}
	\item $y= x \cos(x)^{x}$
	\vfill
	\item $y=\frac{x\sqrt{x^2+1}}{(3x+5)^{7/5}}$
	\vfill
 \end{enumerate}
 \end{enumerate}
 \newpage
 \begin{center} 4.1 Homework Help \end{center}
 \begin{enumerate}
 \item You will need the following formulas. Draw and label a picture for each formula. 
 	\begin{enumerate}
	\item The Pythagorean Theorem
	\vfill
	\item area of a triangle with height $h$ and base $b$
	\vfill
	\item volume of a cube
	\vfill
	\item sides of similar triangles (both right triangles and isosceles triangles)
	\vfill
	\item volume and surface area of a sphere of radius $r.$
	\vfill
	\item volume of a cone with base of radius $r.$
	\vfill
	\item A conical water tank has a height of 10 feet and a radius of 6 feet. Assume that tank is oriented with the point down. If the height of the water in the tank is 4.5 feet high, determine the volume of water in the tank.
	\vfill
	 \item volume of a cylinder with height $h$ and radius $r$
	 \vfill
	 \item A cylindrical water tank has a height of 10 feet and a radius of 6 feet. If the height of the water in the tank is 4.5 feet high, determine the volume of water in the tank.
	 \vfill
	\end{enumerate}
\end{enumerate} 
 
\end{document}

