\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% TiKZ.
\usepackage{tikz, pgfplots}
\usetikzlibrary{calc}
\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
middle, xlabel={$x$}, ylabel={$y$}, axis equal }}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}

% Commands to set various header/footer components.
\makeatletter
\def\doctitle#1{\gdef\@doctitle{#1}}
\doctitle{Use {\tt\textbackslash doctitle\{MY LABEL\}}.}
\def\docdate#1{\gdef\@docdate{#1}}
\docdate{Use {\tt\textbackslash docdate\{MY DATE\}}.}
\def\doccourse#1{\gdef\@doccourse{#1}}
\let\@doccourse\@empty
\def\docscoring#1{\gdef\@docscoring{#1}}
\let\@docscoring\@empty
\def\docversion#1{\gdef\@docversion{#1}}
\let\@docversion\@empty
\makeatother

% Headers and footers layout.
\makeatletter
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % Clears all headers/footers.
\lhead{\baselineskip 30pt
\emph{\@doctitle\hfill\@docdate}
\ifnum \value{page} > 1\relax\else\\
\emph{Name: \rule{3.5in}{1pt}\ \hfill
%Class (circle): \ \  Sync. \hfill Online%\@docscoring
}
\fi}
\rfoot{\emph{\@docversion}}
\lfoot{\emph{\@doccourse}}
\cfoot{\emph{\thepage}}
\renewcommand{\headrulewidth}{0pt}%
\makeatother

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt

% A problem is a section-like command. Use \problem{5} to
% start a problem worth 5 points.
\newcounter{probcount}
\newcounter{subprobcount}
\setcounter{probcount}{0}
\newcommand{\problem}[1]{%
\par
\addvspace{4pt}%
\setcounter{subprobcount}{0}%
\stepcounter{probcount}%
\makebox[0pt][r]{\emph{\arabic{probcount}.}\hskip1ex}\emph{[#1 points]}\hskip1ex}
\newcommand{\thesubproblem}{\emph{\alph{subprobcount}.}}

% Subproblems are an enumerate-like environment with a consistent
% numbering scheme. 
% Use \begin{subproblems}\item...\item...\end{subproblems}
\newenvironment{subproblems}{%
\begin{enumerate}%
\setcounter{enumi}{\value{subprobcount}}%
\renewcommand{\theenumi}{\emph{\alph{enumi}}}}%
{\setcounter{subprobcount}{\value{enumi}}\end{enumerate}}

% Blanks for answers in normal and math mode.
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\mblank}[1]{\underline{\hspace{#1}}}
\def\emptybox(#1,#2){\framebox{\parbox[c][#2]{#1}{\rule{0pt}{0pt}}}}

% Misc.
\renewcommand{\d}{\displaystyle}
\newcommand{\ds}{\displaystyle}
\def\bc{\begin{center}}
\def\ec{\end{center}}


\doctitle{Math 251: Section 4.7 Optimization Prep}
\docdate{Recitation Week 10}
\doccourse{UAF Calculus I}
\docversion{optimization practice}
%\docscoring{\blank{0.8in} / 12}

\begin{document}
\addtolength\itemsep{-1mm}
All of the problems below are homework problems. The goal in Recitation is to get all of these problems \emph{set up.} For each problem you want to (a) draw and label a picture and pick notation, (b) identify what you want to maximize or minimize, (c) write the thing from part (b) as a function of \emph{one} variable. 
\begin{enumerate}
\item[Problem A] You are going to construct an open-topped box with a square base. You need the box to have a volume of $10 \: m^3.$ The material for the base costs $ \$ 5 / m^2$ and the material for the sides costs $\$ 2 / m^2.$ Find the dimensions of the box that minimize the cost.
\vfill
\item[\S 4.7 \# 332.] A pizzeria sells pizzas for a revenue of $R(x)=ax$ and costs $C(x)=b+cx+dx^2,$ with $x$ represents the number of pizzas and $R$ and $C$ are given in dollars. Suppose that $a,b,$ and $d$ are all positive.\\
Find the profit function for the number of pizzas. How many pizzas will maximize the profit?\\
Find the function for profit per pizza. How many pizzas will maximize the profit per pizza?\\
\vfill
\item[\S 4.7 \# 348.] Graph the function $y=5-2x.$ Where is the line $y=5-2x$ closest to the point $(1,1).$\\
\vfill
\newpage
\item[\S 4.7 \# 343.] Find the area of the largest rectangle that fits into the triangle with sides $x=0$, $y=0$, and $\frac{x}{4}+\frac{y}{6}=1.$
\vfill
\item[\S 4.7 \# 319.] You have 400 ft of fencing to construct a rectangular pen for cattle. What are the dimension of the pen that maximize the area?
\vfill
\item[\S 4.7 \# 320.] You have 800 ft of fencing to make a pen for hogs. If you have a river on one sider of your property, what is the dimension of the regangular pen that maximizes the area?
\vfill
\item[\S 4.7 \# 324.] A patient's pulse measures 70 bpm, 80 bpm, and 120 bpm. To determine an accurate measurement ofpulse, the doctor want to know what value minimizes the expression $(x-70)^2+(x-80)^2+(x-120)^2.$ Why would a doctor want to minimize this? What value minimizes it?
\vspace{0.3in}
\end{enumerate}

\end{document}