\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% TiKZ.
\usepackage{tikz, pgfplots}
\usetikzlibrary{calc}
\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
middle, xlabel={$x$}, ylabel={$y$}, axis equal }}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}

% Commands to set various header/footer components.
\makeatletter
\def\doctitle#1{\gdef\@doctitle{#1}}
\doctitle{Use {\tt\textbackslash doctitle\{MY LABEL\}}.}
\def\docdate#1{\gdef\@docdate{#1}}
\docdate{Use {\tt\textbackslash docdate\{MY DATE\}}.}
\def\doccourse#1{\gdef\@doccourse{#1}}
\let\@doccourse\@empty
\def\docscoring#1{\gdef\@docscoring{#1}}
\let\@docscoring\@empty
\def\docversion#1{\gdef\@docversion{#1}}
\let\@docversion\@empty
\makeatother

% Headers and footers layout.
\makeatletter
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % Clears all headers/footers.
\lhead{\baselineskip 30pt
\emph{\@doctitle\hfill\@docdate}
\ifnum \value{page} > 1\relax\else\\
\emph{Name: \rule{3.5in}{1pt}\ \hfill
%Class (circle): \ \  Sync. \hfill Online%\@docscoring
}
\fi}
\rfoot{\emph{\@docversion}}
\lfoot{\emph{\@doccourse}}
\cfoot{\emph{\thepage}}
\renewcommand{\headrulewidth}{0pt}%
\makeatother

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt

% A problem is a section-like command. Use \problem{5} to
% start a problem worth 5 points.
\newcounter{probcount}
\newcounter{subprobcount}
\setcounter{probcount}{0}
\newcommand{\problem}[1]{%
\par
\addvspace{4pt}%
\setcounter{subprobcount}{0}%
\stepcounter{probcount}%
\makebox[0pt][r]{\emph{\arabic{probcount}.}\hskip1ex}\emph{[#1 points]}\hskip1ex}
\newcommand{\thesubproblem}{\emph{\alph{subprobcount}.}}

% Subproblems are an enumerate-like environment with a consistent
% numbering scheme. 
% Use \begin{subproblems}\item...\item...\end{subproblems}
\newenvironment{subproblems}{%
\begin{enumerate}%
\setcounter{enumi}{\value{subprobcount}}%
\renewcommand{\theenumi}{\emph{\alph{enumi}}}}%
{\setcounter{subprobcount}{\value{enumi}}\end{enumerate}}

% Blanks for answers in normal and math mode.
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\mblank}[1]{\underline{\hspace{#1}}}
\def\emptybox(#1,#2){\framebox{\parbox[c][#2]{#1}{\rule{0pt}{0pt}}}}

% Misc.
\renewcommand{\d}{\displaystyle}
\newcommand{\ds}{\displaystyle}
\def\bc{\begin{center}}
\def\ec{\end{center}}


\doctitle{Math 251: Section 4.5 \& 4.6 Homework Help}
\docdate{Recitation Week 9}
\doccourse{UAF Calculus I}
%\docversion{v-practice}
%\docscoring{\blank{0.8in} / 12}

\begin{document}
\addtolength\itemsep{-1mm}

This page contains information and techniques you will need for Sections 4.5 and 4.6.\\
\begin{enumerate}
\item What is a critical point? How do you find them?
\vspace{.5in}
\item What is the importance of critical points? What are they good for?
\vspace{.5in}
\item Draw a graph of a function $f(x)$ with three critical points (at $x=a$, $x=b$ and $x=c$ such that \\
(i) $f'(a)=f'(b)=0$ and $f'(c)$ is undefined,\\
and\\
(i) $f$ has a local minimum at $x=a$, a local maximum at $x=c$ and neither at $x=b.$
\vfill
\item Draw a graph of a function $f(x)$ such that $f(x)<0$ and $f'(x) >0.$
\vfill
\newpage
\item For each function below, find (a) its domain and (b) all its critical points.
	\begin{enumerate}
	\item $f(x)=x^3-2x^2$
	\vfill
	\item $f(x)=x^{1/3}$
	\vfill
	\item $f(x)=\arctan(x)$
	\vfill
	\item $f(x)=\frac{x^2}{x^2-4}$ (Note: $f'(x)=\frac{-8x}{x^2-4}.$)
	\vfill
	\item $f(x)=e^{-x^2}$
	\vfill
	\item $f(x)=\sqrt{x^2-4}$
	\vfill
	\end{enumerate}
\newpage
\item For $f(x)=x^{1/3}$, you should have gotten $x=0$ as the one and only critical point. Explain (in whatever method works for you) \emph{HOW} you will determine the \emph{sign} of $f'(x)$? Repeat the process for $f''(x).$
\vfill
\item Assume the expression below is the second derivative of some function. How will you determine where $y''$ is positive or negative? Are some parts of the expression more important than other parts? What would have happened in the term in the denominator was raised to the \emph{fourth} power instead of the third power?\\
$$y''=\frac{8(3x^2+4)}{(x^2-4)^3}$$
\vfill
\item Sketch a graph with two vertical asymptotes and one horizontal asymptote.
\vfill
\item Write a formula for a function $f(x)$ such that $f(x)$ has asymptotes $x=1$, $x=4$ and $y=2.$
\vspace{1in}
\newpage
\item Can a function have more than one \emph{horizontal} asymptote? Explain.
\vfill
\item Can a function with a horizontal asymptote ever cross that asymptote? Explain.
\vfill
\item Evaluate each limit below and \emph{justify} your answer. Your justification can be in words, using a graph, and/or numerical (or all of the above). 
	\begin{enumerate}
	\item $\displaystyle \lim_{x \to 2^+} \frac{5}{x-2}$\\ \vfill
	\item $\displaystyle \lim_{x \to 2^-} \frac{5}{x-2}$\\ \vfill
	\item $\displaystyle \lim_{x \to 2} \frac{5}{x-2}$\\ \vfill
	
	\item $\displaystyle \lim_{x \to \infty} \frac{5}{x-2}$\\ \vfill
	\item $\displaystyle \lim_{x \to -\infty} \frac{5}{x-2}$\\ \vfill
	\item $\displaystyle \lim_{x \to \infty} \left(8+\frac{5}{x-2}\right)$\\ \vfill
	\item $\displaystyle \lim_{x \to \infty} \left(x+\frac{5}{x-2}\right)$\\ \vfill
	\end{enumerate}	
\end{enumerate}
\end{document}

\vfill
\item Graph $y=e^x$ and $y=e^{-x}$ on the same set of axes. Label the points associated with $x=-1,$ $x=0,$ and $x=1$ on both graphs.
\vfill
\item On separate axes, graph $y=x^2$, $y=\sqrt{x}$, $y=1/x^2.$ 
\vfill
\item For all of the graphs above, describe the \emph{end behavior} of the graphs. This means, describe what happens for really large $x$ values (think $10^{100}$ and really small $x$-values (think $-10^{100}.$ Note ``small" means toward negative infinity, not close to zero.

\end{enumerate}
\end{document}