
\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% TiKZ.
\usepackage{tikz, pgfplots}
\usetikzlibrary{calc}
\pgfplotsset{compat = newest}
 
\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
middle, xlabel={$x$}, ylabel={$y$}, axis equal
}}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}

% Commands to set various header/footer components.
\makeatletter
\def\doctitle#1{\gdef\@doctitle{#1}}
\doctitle{Use {\tt\textbackslash doctitle\{MY LABEL\}}.}
\def\docdate#1{\gdef\@docdate{#1}}
\docdate{Use {\tt\textbackslash docdate\{MY DATE\}}.}
\def\doccourse#1{\gdef\@doccourse{#1}}
\let\@doccourse\@empty
\def\docscoring#1{\gdef\@docscoring{#1}}
\let\@docscoring\@empty
\def\docversion#1{\gdef\@docversion{#1}}
\let\@docversion\@empty
\makeatother

% Headers and footers layout.
\makeatletter
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % Clears all headers/footers.
\lhead{\baselineskip 30pt
%\emph{\@doctitle\hfill\@docdate}
\emph{\@docdate\hfill\@doctitle}
\ifnum \value{page} > 1\relax\else\\
\emph{Name: \rule{3.5in}{1pt}\hfill \@docscoring}\fi}
\rfoot{\emph{\@docversion}}
\lfoot{\emph{\@doccourse}}
\cfoot{\emph{\thepage}}
\renewcommand{\headrulewidth}{0pt}%
\makeatother

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt

% A problem is a section-like command. Use \problem{5} to
% start a problem worth 5 points.
\newcounter{probcount}
\newcounter{subprobcount}
\setcounter{probcount}{0}
\newcommand{\problem}[1]{%
\par
\addvspace{4pt}%
\setcounter{subprobcount}{0}%
\stepcounter{probcount}%
\makebox[0pt][r]{\emph{\arabic{probcount}.}\hskip1ex}\emph{[#1 points]}\hskip1ex}
\newcommand{\thesubproblem}{\emph{\alph{subprobcount}.}}

% Subproblems are an enumerate-like environment with a consistent
% numbering scheme. 
% Use \begin{subproblems}\item...\item...\end{subproblems}
\newenvironment{subproblems}{%
\begin{enumerate}%
\setcounter{enumi}{\value{subprobcount}}%
\renewcommand{\theenumi}{\emph{\alph{enumi}}}}%
{\setcounter{subprobcount}{\value{enumi}}\end{enumerate}}

% Blanks for answers in normal and math mode.
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\mblank}[1]{\underline{\hspace{#1}}}
\def\emptybox(#1,#2){\framebox{\parbox[c][#2]{#1}{\rule{0pt}{0pt}}}}

% Misc.
\renewcommand{\d}{\displaystyle}
\newcommand{\ds}{\displaystyle}
\def\bc{\begin{center}}
\def\ec{\end{center}}
\def\be{\begin{enumerate}}
\def\ee{\end{enumerate}}


\doctitle{Math 251: Quiz 4}
\docdate{September 22, 2023}
\doccourse{UAF Calculus I}
\docversion{v-1 async}
\docscoring{\blank{0.8in} / 25}
\begin{document}
%\textbf{Please circle your instructor's name:} \hfill Leah Berman  \hfill   Jill Faudree\\

There are 25 points possible on this quiz.  {\it You should be able to complete it without using your notes or textbook -- this is practice for your exams!} If you needed to look something up, you should to me about questions you might have.  {\bf Show all work for full credit} and use some words or sentences to help communicate your answers. {\bf Do not use a calculator.}

\problem{8} Use the \emph{limit definition} of the derivative to find the derivative of $g(x)=x+\frac{3}{x}$. \emph{No credit will be awarded a solution that does not use the definition below.} Show all your work clearly, step by step, using correct notation.\\
$$g'(x) := \lim_{h \to 0} \frac{g(x+h) - g(x)}{h}$$
\vfill
\problem{6} A ball is thrown upwards into the air. Its height, in feet, after $t$ seconds is given by the function $s(t) = 40t - 16 t^{2}$
\begin{subproblems}
\item Find the average velocity of the ball over the time interval from $t=1$ to $t=2.$ Include units with your answer.\\
\vspace{0.8in}
\item Find the instantaneous velocity of the ball when $t=2.$ Include units with your answer.\\
\vspace{0.8in}
\end{subproblems}

\newpage
\problem{5} The graph of $f(x)$ is below. On the same set of axes, make a rough sketch of the graph of $f'(x)$. If they exist, indicate any asymptotes with dashed lines. Use open circles to show points where the derivative is not defined, if any. {\it Make sure you are writing darkly enough that I can see your graph clearly! (Double-check your scan before you submit.)}
\begin{center}
\begin{tikzpicture}
%cubic
\begin{axis}[xscale=1.2, thick, my style, xtick={-4,-3,-2,...,3,4,5, 6, 7}, ytick={-4,-3,...,5},xmin=-4, xmax=7, ymin=-4, ymax=5, minor y tick num=1, minor x tick num=1, 
mark size=3.0pt, grid = major]
\addplot[ultra thick, -,domain=-2:1, samples=100]{1+2*x};
\addplot[ultra thick,domain=-4:-2, samples=100, <-]{-3};
\addplot[ultra thick, ->,domain=1:7, samples=100]{-(2.1*(x-1)^(1/2)+2)+5};
\end{axis}
\end{tikzpicture}\end{center}

\problem{6} Use the derivative rules to find the derivative for each function below. \emph{Do not simplify your answer.}
\begin{subproblems}
\item $f(x)=(\sin{x})(3x^{2} - 5x + 6)$ 
\vfill
\item $g(x)=4x^{1/5}+\frac{9}{x^3} +\sqrt{3}+10x$
\vfill
\end{subproblems}

\end{document}