\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace, adjustbox}
\usepackage{array%,tikz, pgfplots
}

\usepackage{tikz, pgfplots}
\usetikzlibrary{calc}
%\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
%middle, xlabel={$x$}, ylabel={$y$}, axis equal }}
%
\pagestyle{fancy} 
\lfoot{UAF Calculus I}
\rfoot{3-6 \& 3-7}


\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\begin{document}
\setlength{\parindent}{0cm}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
\vspace*{-0.7in}
\begin{center}
 {\large{ \sc{Section 3.6: Logarithmic Differentiation}}}
\end{center}
\begin{enumerate} 	
\item Find the derivative of
	\begin{enumerate}
	\item $y=(3x-x^5)^{2/3}(x-\tan(x))^5.$\\
	\vfill
	\item Find the derivative of $y=(\sin (x))^x.$
	\vfill
	\end{enumerate}
\newpage
\begin{center}
 {\large{ \sc{Section 3.7: Rates of Change in the Natural and Social Sciences}}}
\end{center}
\item A ball is tossed straight up into the air. It has a velocity
at time $t=0$ seconds of 5 meters per second.  It undergoes a constant
acceleration due to gravity of $-9.8$ meters per second per second,
m/s$^2$.   The height of the ball can be written in the form
\[
h(t) = at + b t^2
\]
where $h$ is measured in meters, time is measured in seconds, and $a$
and $b$ are certain constants.
\begin{enumerate}
\item Determine the values for the constants.
\vfill
\item What is the height of the ball at time $t=0$? At $t=1$?
\vfill
\item At what times is the ball at height $0$?
\vfill
\item What is the average velocity of the ball over the time interval
$[0.2,0.21]$?
\vfill
\item What is the average velocity of the ball over the time interval
$[0.2,0.201]$?
\vfill
\item What is the instantaneous velocity of the ball at time $t=0.2$??
\vfill
\item At what time $t$ is the ball motionless?
\vfill
\item What is the velocity of the ball at time $t=0$? At $t=0.1$? At $t=1$?
\vfill
\end{enumerate}
\newpage
\item A stone is thrown in a pond and a circular ripple travels
outward at a speed of 60 cm/s.  Determine the rate of change of
area inside the ripple at time $t=1$ second and at time $t=2$ seconds.
\vfill
\item A population of bacteria starts at 500 cells and doubles every
30 minutes.  Find a function $P(t)$ that describes this situation.
Then compute the rate of change of the bacteria population at time $t=60$ minutes.
\vfill
%\aproblem A one-meter rod has non uniform mass.  The mass of the rod
%from one end to distance $x$ along it is
%\[
%m(x) = x+\frac{1}{3}\sqrt{x}
%\]
%where mass is measured in grams and $x$ is in centimeters.
\newpage
\item A population of caribou is growing, and its population is
\[
P(t) = 4000\frac{3e^{t/5}}{1+2e^{t/5}}.
\]
\begin{enumerate}
\item What is the population at time $t=0$?
\vfill
\item Determine the rate of change of the population at any time $t$.
\vfill
\item Determine the rate of change of the population at time $t=0$ years.
\vfill
\item Determine the long term population.
\vfill
\end{enumerate}

\end{enumerate}
\end{document}