\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx, pgfplots} 
\usepackage[all]{xy}
\usepackage{polynom,tabularx} 
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array}
\usepackage{pgf,tikz}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}

\usetikzlibrary{calc}

\pgfplotsset{compat=1.6}

\pgfplotsset{soldot/.style={color=blue,only marks,mark=*}} \pgfplotsset{holdot/.style={color=blue,fill=white,only marks,mark=*}}

\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\renewcommand{\d}{\displaystyle}



\pagestyle{fancy} 
%\lfoot{Uses a calculator}
\rfoot{Review: Chapters 3 \& 4}

\begin{document}

\vspace*{-0.7in}

\begin{center}
  \large
  \sc{Recitation: Review of Chapters 3 \& 4}\\
\end{center}
\be


%all info to graph
\item $f(x)=(x-4)\sqrt[3]{x}=x^{4/3}-4x^{1/3}; \quad f'(x)=\frac{4(x-1)}{3x^{2/3}}; \quad f''(x) = \frac{4(x+2)}{9x^{5/3}}.$
\be
  \item Find the critical numbers of $f(x).$
  \vfill
   \item Find the open intervals on which the function is increasing or
    decreasing. \vfill
    
    \item Classify all critical points -- using the \textbf{first derivative test}.  \vfill
     \item Classify all critical points -- using the \textbf{second derivative test}.  \vfill
    \newpage
    From the other side: $f(x)=(x-4)\sqrt[3]{x}=x^{4/3}-4x^{1/3}; \quad f'(x)=\frac{4(x-1)}{3x^{2/3}}; \quad f''(x) = \frac{4(x+2)}{9x^{5/3}}.$
   
 \item Find the open intervals on which the function is concave up or
    concave down.  \vfill
    
  \item Find the inflection points.   \vfill
  
  \item Sketch the graph.
  \vspace{4in}
\ee

\newpage

%page 2
%related rate
\item A paper cup has the shape of a cone with height 10 cm and radius 3 cm (at the top). If water is poured into the cup at a rate of $2\: \text{cm}^3/\text{sec}$, how fast is the water level rising when the water is 5 cm deep? (Volume of a cone is: $V=(1/3) \pi r^2 h.$)
\vfill
%optimization
\item Find the dimensions of the rectangle of maximum area that can be inscribed in an equilateral triangle of side 20 cm if one side of the rectangle likes on the base of the triangle.
\vfill
\newpage
%max-min closed intervals
\item Determine the absolute maximum and absolute minimum of  $\d f(x) = \frac{1}{x} + x$ on $[1/2,4].$
\vspace{3.5in}
\item Below is the graph of the DERIVATIVE, $h'(x)$ of $h(x).$\\
\begin{tikzpicture}[scale=.5]
\draw[->] (-3,0) -- (4.2,0) node[right] {$x$};
      \draw[->] (0,-3) -- (0,4.2) node[above] {$y$};
      \draw[scale=0.5,domain=-3:4,smooth,variable=\x,ultra thick] plot ({\x},{((0.5)^\x-1)});
      %\draw[scale=0.5,domain=-3:3,smooth,variable=\y,red]  plot ({\y*\y},{\y});
\end{tikzpicture}
	\begin{enumerate}
	\item Does $h(x)$ have any critical points? If so, what are they?
	\vfill
	\item Does $h(x)$ have any local extrema? If so, where do they occur and what type (min/max)?
	\vfill
	\item Can you determine if $h(x)$ is concave up or down?
	\vfill
	\end{enumerate}
\newpage
\item A circular metal plate is being heated in an oven.
The radius of the plate is increasing at a rate of 0.01 cm/min
when the radius is 50cm.  How fast is the area of the plate increasing?
\vfill
\item A Norman window is has a rectangular base and a semi-circle on
top.  What dimensions of the window minimize the perimeter if the area
of the window is to be 4 ft$^2$.
\vfill
\item Find the domain of the function $f(x)=\frac{\sin(5x)}{x^2+x}$ and identify any vertical or horizontal asymptotes. Justify your answers.\\

\vspace{2.5in}
\ee
\end{document}
