\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol, adjustbox}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage[shortlabels]{enumitem}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}
\pagestyle{fancy} 
\lfoot{UAF Calculus I}
\rfoot{5-4}

\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\begin{document}
\setlength{\parindent}{0cm}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
\vspace*{-0.7in}
\begin{center}
  \Large \sc{Section 5-4: Indefinite Integrals and the Net Change Theorem}
\end{center}

\be
\item Compute $\int x^2(3-x)\; dx$
\vfill

\item Compute $\int 9\sqrt{x} - 3 \sec(x)\tan(x)\; dx$
\vfill

\item Find an antiderivative of $f(x)=\frac{1}{x^2}$
that does not have the form $-1/x + C$.
\vfill



\item Snow is falling on my garden at a rate of
\[
A(t) = 10 e^{-2 t}
\]
kilograms per hour for $0\le t\le 2$, where $t$ is measured in hours.
\begin{enumerate}
\item Find $A(1)$ and interpret in the context of the problem.
\vfill
\item If $m(t)$ is the total mass of snow on my garden, how are $m(t)$
and $A(t)$ related to each other?
\vfill
\item What does $m(2)-m(0)$ represent?
\vfill
\item Find an antiderivative of $A(t)$.
\vfill
\item Compute the total amount of snow accumulation from $t=0$ to $t=1$.
\vfill
\item Compute the total amount of snow accumulation from $t=0$ to $t=2$.
\vfill
\newpage
\item From the information given so far, can you compute $m(2)$?
\vfill
\item Suppose $m(0)=9$.  Compute $m(1)$ and $m(2)$.
\vfill
\end{enumerate}

\item A airplane is descending.  Its rate of change of height
is $\d r(t) = -4 t + \frac{t^2}{10}$ meters per second.  
\begin{enumerate}
\item if $A(t)$ is the altitude of the airplane in meters, 
how are $A(t)$ and $r(t)$ related?
\vfill
\item What physical quantity
does $\d \int_1^3 r(t)\; dt$ represent?
\vfill
\item  Compute $A(3)-A(1)$.
\vfill
\item What is the height of the plane when $t=3$?
\vfill
\end{enumerate}
\vfill
\item
Gravel is being added to a pile at a rate of rate of $1+t^2$
tons per minute for $0\le t\le 10$ minutes. If $G(t)$ is the
amount of gravel (in tons) in the pile at time $t$, compute
$G(10)-G(0)$.
\vfill
\ee
\end{document}
