% !TEX TS-program = pdflatexmk
\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,hyperref}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl}
\usepackage{enumitem}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Calc I Syllabus},
    pdfpagemode=FullScreen,
    }

\def\mailto#1{\href{mailto:#1}{#1}}

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt
\def\tableindent{\hskip 0.5 in}
\def\ts{\hskip 1.5 em}

\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH F251: Calculus I (in person)}}
\rhead{\large\sf\textbf{Spring 2023 Syllabus}}

\newcommand{\localhead}[1]{\par\smallskip\textbf{#1}\nobreak\\}%
\def\heading#1{\localhead{\large\emph{#1}}}
\def\subheading#1{\localhead{\emph{#1}}}

\newenvironment{clist}%
{\bgroup\parskip 0pt\begin{list}{$\bullet$}{\partopsep 4pt\topsep 0pt\itemsep -2pt}}%
{\end{list}\egroup}%

\begin{document}

% \heading{Course Description}

\strut\par\vskip-12pt
\heading{Essential Information}

\vskip -12pt
\strut\hbox to \hsize{\tableindent\vtop{\halign{#\hfill\ts&#\hfil\cr
{\emph{Instructors}}&Dr. Julie McIntyre (\S 901) \& Dr. Jill Faudree (\S 902 \& 903)\cr
\strut & \cr

{\emph{Website}}&\url{https://uaf-math251.github.io}\cr
\strut & \cr
\emph{Prerequisite} & MATH F151X and MATH F152X; or MATH F156X; or placement.\cr
\strut & \cr
{\emph{Required Text}} &\textit{OpenStax Calculus Volume 1} by G. Strang \& E. Herman,\cr
&\url{https://openstax.org/details/books/calculus-volume-1} \cr
&(optional print copy)\texttt{ISBN-13: 978-1938168024}\cr
  \strut & \cr
{\emph{Grades}}&(Canvas) \url{https://www.uaf.edu/uaf/current/canvas.php}\cr
 \strut & \cr
 {\emph{Class Discord}}&\url{https://nookbot.uaf.edu/}\cr
 \strut & \cr
 {\emph{Dr. McIntyre}}&Email: jpmcintyre@alaska.edu\cr
 &Office: Chapman 201D\cr
 \strut & \cr 
 {\emph{Dr. Faudree}}&Email: jrfaudree@alaska.edu\cr
 &Office: Chapman 306B\cr
 \strut & \cr 
 }
\hfil}}

\vskip -12pt
\heading{Description, Course Goals \& Student Learning Outcomes}
Calculus is one of mathematics' premiere computational tools.  It has
pervasive applications in all the sciences and is part of the UAF core 
curriculum.  The two principal tools of calculus are differentiation and integration. Differentiation concerns how changes in one variable affect another.
How does a population of bacteria change as time changes?  
How does the temperature of the ocean change as depth increases?
Integration, on the other hand, is a kind of reverse process to
differentiation. 

Students completing the course will have the mathematical foundation to be successful in Calculus II and other courses
requiring this background.  Specifically, students will
\begin{clist}
\item understand the role of limits in the definition of a derivative 
and be able to compute elementary derivatives from this definition,
\item understand the definition of a continuous function and identify
continuous/discontinuous functions,
\item develop the skills to compute standard derivatives,
\item apply derivatives to common types of applied problems,
\item understand the definition of the the definite integral,
\item apply the Fundamental Theorem of Calculus to
compute definite integrals,
\item apply integration to common types of applied problems.
\end{clist}

\newpage

\heading{Class Time}
There are four hours of class meetings with your primary instructor every week (MWThF). This time will be used to discuss new topics in Calculus and for a weekly quiz on Thursdays. The last 30 minutes of the Thursday class will be spent with a teaching assistant (TA) going over the weekly quiz (Yes! We will go over the quiz immediately!) so all students can leave knowing what material on that quiz has been mastered, how to work each problem correctly,  and what topics need additional study. 

The Tuesday Recitation (MATH F251L) will initially be spent helping students get started on first-of-semester tasks. Starting on Week 3, the Tuesday class is explicitly devoted to bolstering the underlying non-Calculus skills that are nevertheless essential to success in Calculus such as: graphing, algebra, trigonometry, exponential and logarithmic functions, and inverse functions. It will also include additional strategic homework/quiz/test prep. As a concrete example, one of the things we will do in Recitation is go over the non-Calculus math skills needed to complete the up-coming homework so that students can focus on the Calculus instead of getting bogged down in algebra or trigonometry.

\heading{Tentative Schedule}
The course website contains a \href{https://docs.google.com/spreadsheets/d/e/2PACX-1vQGc6J1T0q0ik53Vks8LatvLNG9OMWIlA9mkIOz6BWO9KZecpv0yYPTKDhgKxS-UxQ809bjz4kUVgbk/pubhtml?gid=0&single=true}{schedule} for the semester listing
the topics to be covered each class, the dates each assignment is due,
the topics of every quiz, and so forth. You should consult this schedule
routinely.  We may make minor adjustments to the schedule, which
will be announced in advance.

\heading{Office Hours and Communication}
Instructors and TAs will schedule formal office hours,
which will be listed on web sites accessible from the main
course webpage. Any office hours in the \href{https://uaf.edu/dms/mathlab/}{Math Tutoring Lab} are open to \emph{all} Calculus I students regardless of who is their instructor of record. Students can also schedule meetings with their instructor outside of regular office hours. 

We will use Canvas to send announcements. If we (your instructor/TA) need to contact you, we will first try to do this in class. Our second method will be to send an email to you via Canvas. Thus, you will want to make sure that the email address in Canvas is one that you check regularly. Note that in Canvas it is possible to set up text alerts. However, you must login to Canvas and adjust the setting for your account. Neither email nor text alerts are automatic.



\heading{Evaluation and Grades}
Grades are determined as follows; 
each component of the grade is discussed subsequently in
the syllabus.
 
\begin{multicols}{2}

\begin{tabular}{|c|c|}
\hline
Class Participation& 7.5\%\\
\hline
(Written) Homework& 7.5\% \\
\hline
Quizzes& 15\% \\
\hline
Midterm 1 & 15\% \\
\hline
Derivative Proficiency& 7.5\%\\
\hline
Midterm 2 & 15\%  \\
\hline
Integral Proficiency& 7.5\%\\
\hline
Final Exam& 25\% \\
\hline
total& 100\%\\
\hline
\end{tabular}

\vskip 6pt
Letter grades will be assigned according to the following scale.
This scale is a guarantee; the instructors reserve the right to lower the thresholds. 

\def\sts{\hskip 0.5em}
\strut\hbox to\hsize{\vbox{\halign{#\hfil\sts&#\hfil\ts&#\hfil\sts&#
\hfil\ts&#\hfil\sts&#\hfil   \cr
A+ & 97--100\% & C+ & 77--79\% & F  & $<$ 60\%\cr

A & 93--96\% &  C & 70--76\%&&\cr
A- & 90--92\% & C- & not given&&\cr
B+ & 87--89\% & D+ & 67--69\%&&\cr
B &  83--86\% & D & 63--66\%&&\cr
B- & 80-82\% & D- & 60--62\%&&\cr
}}\hfil}
\end{multicols}

\heading{Online Course Materials}
All materials for this course are posted online. (See Table \ref{wheretofind} below.) \\

\begin{table}[h]
\centering
\begin{tabular}{rl}
where to find it&what you are looking for\\
\hline \hline
&syllabus and day-by-day schedule for the semester\\
&ALEKS logistics\\
&homework problem sets\\
public Calculus I webpage&practice quizzes, proficiencies, midterms, final exams\\
\href{https://uaf-math251.github.io/}{https://uaf-math251.github.io/}&solutions to practice quizzes, proficiencies, midterms, final exam\\
&videos\\
&recitation worksheets with solutions \& videos\\
&textbook\\
&in-class worksheets with solutions\\
\hline
&announcements and reminders\\
&link to Gradescope (to turn in homework)\\
\href{https://www.uaf.edu/uaf/current/canvas.php}{Canvas}& complete solutions to homework\\
& your grades\\
&textbook\\
%\hline
%see your instructor&in-class materials for your section\\
\end{tabular}
\caption{}
\label{wheretofind}
\end{table}

%\heading{Weeks 1 \& 2 Logistics}
%The first week of the course is devoted to prerequisite review. Consequently, the homework and quiz mechanics for the first two weeks are different from that of the remainder of the semester.
%
%In the first week, instead of the usual written homework, you will be
%working with a program called ALEKS to refresh precalculus skills, and the first
%quiz will be an ALEKS-based assessment. (See \href{https://uaf-math251.github.io/week1-ALEKS.html}{Week 1 Details} for step-by-step instructions.)\\ 
%During the first weeks you will:
%\begin{clist}
%\item enroll in the UAF MATH 251 Spring 2022 Cohort of ALEKS PPL\\
%class code: \textbf{ERD3E-L6JKM}
%\item complete an initial placement test (approx 1-2 hours) by \textbf{Tuesday August 30} at 11:59pm \\
%(Note: We will start this in class on Tuesday. Most people will finish during class. Those who do not will just finish up later that day. Finishing the initial placement on time is worth 10 points added to Quiz 1, your proctored ALEKS score.),
%\item complete 90\% of the ALEKS pie \: OR \: spend 5 hours in Learning Mode by Monday, September 5 at 11:59pm which will count as your first homework grade,
%\item sign-up by Monday, September 5 for a 2-hour Tuesday time-slot to take Quiz 1, 
%\item complete an ALEKS assessment (approx 1-2 hours) on Tuesday, September 6 which will count as Quiz 1.
%\end{clist}
%The standard Tuesday class on September 6 is cancelled and instead you will go to Rasmuson Library Room 301 to take your ALEKS assessment at whatever time slot you reserved. 

\heading{Class Participation}
Attendance and participation in class is an important part of mastering the material in Calculus (and all of your classes). Class attendance is one of the best predictors of overall course performance regardless of subject. For this reason, we want to incentivize this aspect of your education. A student is counted as having successfully participated in class if that student was in class on-time and was an active participant during the whole class. Being an active participant includes engaging in classroom tasks such as individual or group worksheets, classroom discussions, and other classroom activities. Your class participation score will be calculated as the percent of classes in which you were an active participant. 

Let your instructor know if you have missed class for an excused reason.

\heading{Homework}
Homework assignments typically consist of a selection of problems at the end of each section of our textbook and a few additional problems. Homework is written (on paper or tablet) and turned in via Gradescope which is accessed from Canvas.  Help with scanning homework can be found under \href{https://uaf-math251.github.io/techHelp.html}{Technology Help} on the course webpage. Assignments are due most Mondays and Wednesdays (by 11:59 PM) in advance of the Thursday quiz. Complete worked solutions to all problems are provided in advance on Canvas. Consequently, your homework will be graded based on \emph{effort} and \emph{completion}.  All students should earn 100\% of their homework points!

The list of homework problems and homework guidelines can be found at the \href{https://uaf-math251.github.io/newhomework.html}{Homework} link on the course webpage.

Clearly, it is possible to short-circuit the homework by copying the solutions. It should also be clear that (a) this is a bad idea and (b) your instructor/TA will know you have done this. Our goal in providing answers and solutions is to foster the use of homework as a \emph{learning experience}. 

\textcolor{blue}{Your first written homework assignment is due Monday January 23.} Note that this is the last day to turn in this homework assignment. You should plan to turn it in before this deadline.

\heading{Quizzes}
Quizzes 2 through 10 are paper quizzes and are given on Thursdays in the middle third of the class. Students will be given the opportunity to correct their quizzes in the last third of the Thursday class and can earn points back on their quiz for doing so \emph{accurately}. The weekly quiz will cover the material taught in the classes held since the previous quiz; specific topics can be found in the schedule on the course website.  Quiz 1 and Quiz 11 are given online using a program called ALEKS. 

Quizzes are equally weighted, and are given under testing conditions; books, notes, and calculators are not allowed unless otherwise stated. Your performance on the quizzes \emph{prior to corrections} is the best indicator of how well you are learning the course material and much more accurate than your homework score.

Make-up Quizzes are possible provided there is a documented, excused absence. Always contact your instructor if you miss a quiz.

\textcolor{blue}{Quiz 1 is Tuesday January 24.} It will be given in Rasmuson Library Room 301. You will sign-up for a 2-hour time window to take your assessment \href{https://aleks-testing.youcanbook.me/}{here.} If you like, you can login to your ALEKS course in advance and/or see what the process will be like by visiting the ALEKS info link on the public webpage \href{https://uaf-math251.github.io/week1-ALEKS.html}{here}.


\heading{Recitations}
The Tuesday Recitation is taught by a teaching assistant (TA), graduate students from the Math  Department who have experience teaching Calculus. Starting in Week 3, the Tuesday class is explicitly devoted to bolstering the underlying non-Calculus skills that are nevertheless essential to success in Calculus such as: graphing, algebra, trigonometry, exponential and logarithmic functions, and inverse functions. It will also include additional strategic homework/quiz/test prep. As a concrete example, one of the things we will do in Recitation is go over the non-Calculus math skills needed to complete the up-coming homework so that students can focus on the Calculus instead of getting bogged down in algebra or trigonometry.

For students who earn high scores (80\% or higher without the added extra credit) on the Tuesday, January 24 ALEKS assessment \textbf{and} who have completed every assignment by the end of Week 2 at an 80\% level or higher \textbf{and} who have no unexcused absences, the Recitation will be optional. If Recitation is optional, the Class Participation portion will be calculated in two ways -- including the Recitation and not  including it. The higher of the two percentages will used. All students are allowed and encouraged to attend Recitation.

\heading{Midterms}
There are two midterm exams this semester, to be held on the dates
in the schedule on the course website. Note that the course webpage contains all previous Midterms (with solutions) so a student can know in advance what these are like and has lots of opportunity for practice. The midterms are the same 
for all sections; they are prepared and approved by all instructors teaching the course. 

Make-up midterms will be given only for documented excused absences. Always contact your instructor if you miss a midterm.

\heading{Proficiencies}
A proficiency is an assessment covering a routine mechanical skill.  In
this course we have two of these, one for derivatives and one for 
integrals, on the dates listed in the online schedule. Note that the course webpage contains all previous proficiencies (with solutions) so a student can know in advance what these are like and has lots of opportunity for practice.
Proficiencies will be graded on a binary scale for each problem
(no partial credit).  

We have designed the grading structure in this course to prioritize and reward effort. Thus, you will have the opportunity to retake each proficiency. The highest of the scores will be used to calculate a student's grade. 

\heading{Final Exam} 
The cumulative final exam will be held at the day/time listed in the
online schedule. Note that the course webpage contains all previous final exams (with solutions) so a student can know in advance what these are like  and has lots of opportunity for practice.
A make-up final exam will be given only in extenuating circumstances, for documented and excused reasons at the discretion of the instructors.

\heading{Tutoring and Resources}
\vskip -30pt\strut
\begin{clist}
	\item The Math and Stat Lab, Chapman Building Room 305, offers tutors. 
	See 

	\url{https://www.uaf.edu/dms/mathlab/} for schedules and availability.
	\item One-on-one (or small group) tutoring is available in 
Chapman Building Room 201. You must schedule an
appointment; see \url{https://www.uaf.edu/dms/mathlab/}.
	\item Student Support Services offers free tutoring in many subjects to students who qualify for their program.
	\item ASUAF offers private tutoring for a small fee (based on student income).
\end{clist}

\heading{Rules and Policies}
\vskip -20pt
%\subheading{Participation and Attendance}
%Class and recitation attendance is mandatory. Students who stop participating in the course will be withdrawn. Examples of inadequate participation include,
%but are not limited to:
%\begin{clist}
%\item missing class five times
%\item not completing or not turning in \textbf{three} written homework assignments
%\item failing to participate in classroom activities
%\item repeatedly failing tests and quizzes with no attempt at remediation
%\end{clist}

%\subheading{Disability Services}
%The Office of Disability Services implements the
%Americans with Disabilities Act (ADA), and ensures that UAF students
%have equal access to the campus and course materials. The instructors will work with
%the Office of Disability Services (208 Whitaker, 474-5655) to provide
%reasonable accommodations to students with disabilities.

%\subheading{Student Protections and Services}
%Every qualified student is welcome in my classroom.  As needed, I am happy to
%work with you, disability services, veterans' services, rural student services,
%etc to find reasonable accomodations. Students at this university are protected
%against sexual harassment and discrimination (Title IX), and minors have
%additional protections. \textit{As required,} if I notice or am informed
%of \textit{certain types} of misconduct, then I am required to report it
%to the appropriate authorities.  For more information on your rights as a
%student and the resources available to you, please go to the following site:
%\texttt{https://cms-test.alaska.edu/handbook/}.

This course is listed as a General Education Math Course. As such this course is expected to meet the 4 general learning outcomes. 

\begin{enumerate}
\item Build knowledge of human institutions, sociocultural processes, and the physical and natural works through the study of mathematics.  Competence will be demonstrated for the foundational information in each subject area, its context and significance, and the methods used in advancing each.

\item Develop intellectual and practical skills across the curriculum, including inquiry and analysis, critical and creative thinking, problem solving, written and oral communication, information literacy, technological competence, and collaborative learning. Proficiency will be demonstrated across the curriculum through critical analysis of proffered information, well-reasoned solutions to problems or inferences drawn from evidence, effective written and oral communication, and satisfactory outcomes of group projects.

\item Acquire tools for effective civic engagement in local through global contexts, including ethical reasoning, intercultural competence, and knowledge of Alaska and Alaska issues.  Facility will be demonstrated through analyses of issues including dimensions of ethics, human and cultural diversity, conflicts and interdependencies, globalization, and sustainability.   

\item Integrate and apply learning, including synthesis and advanced accomplishment across general and specialized studies, adapting them to new settings, questions and responsibilities, and forming a foundation for lifelong learning. Preparation will be demonstrated though production of a a creative or scholarly product that requires broad knowledge, appropriate technical proficiency, information collection, synthesis, interpretation, presentation and reflection.
\end{enumerate}

\subheading{Incomplete Grade} 
Incomplete (I) will only be given in
  DMS courses in cases where
  the student has completed the majority (normally all but the last
  three weeks) of a course with a grade of C or better, but for
  personal reasons beyond his/her control has been unable to complete
  the course during the regular term. Negligence or indifference are
  not acceptable reasons for the granting of an incomplete
  grade. 

\subheading{Late Withdrawals} 
A withdrawal after the deadline
  (currently 9 weeks into the semester) from a DMS course will
  normally be granted only in cases where the student is performing
  satisfactorily (i.e., C or better) in a course, but has exceptional
  reasons, beyond his/her control, for being unable to complete the
  course. These exceptional reasons should be detailed in writing to
  the instructor, department head and dean.

\subheading{No Early Final Examinations}
 Normally, a student will not be
  allowed to take a final exam early. Exceptions can be made by
  individual instructors, but should only be allowed in exceptional
  circumstances and in a manner which doesn't endanger the security of
  the exam.

\subheading{Academic Dishonesty}
Academic dishonesty, including cheating and plagiarism, will not
be tolerated.  It is a violation of the Student Code of Conduct
and will be punished according to UAF procedures.

 %\begin{center} \textsc{Syllabus Addendum} \end{center}
 
 \noindent{\bf COVID-19 statement:} Students should keep up-to-date on the university's policies, practices, and mandates related to COVID-19 by regularly checking this website: \url{https://sites.google.com/alaska.edu/coronavirus/uaf?authuser=0}

Further, students are expected to adhere to the university's policies, practices, and mandates and are subject to disciplinary actions if they do not comply.

\noindent{\bf Student protections statement:} UAF embraces and grows a culture of respect, diversity, inclusion, and caring. Students at this university are protected against sexual harassment and discrimination (Title IX). Faculty members are designated as responsible employees which means they are required to report sexual misconduct. Graduate teaching assistants do not share the same reporting obligations. For more information on your rights as a student and the resources available to you to resolve problems, please go to the following site: \url{https://catalog.uaf.edu/academics-regulations/students-rights-responsibilities/}.

\noindent{\bf Disability services statement:} We will work with the Office of Disability Services to provide reasonable accommodation to students with disabilities.

\noindent{\bf Student Academic Support:}
\begin{itemize}
\setlength\itemsep{0em}
        \item Speaking Center (907-474-5470,
        \mailto{uaf-speakingcenter@alaska.edu}, Gruening 507)
\item Writing Center (907-474-5314, \mailto{uaf-writing-center@alaska.edu}, Gruening 8th floor)
\item UAF Math Services, \mailto{uafmathstatlab@gmail.com}, Chapman Building (for math fee paying students only)
\item Developmental Math Lab, Gruening 406
\item The Debbie Moses Learning Center at CTC (907-455-2860, 604 Barnette St, Room 120,\\ \mailto{https://www.ctc.uaf.edu/student-services/student-success-center/})
\item For more information and resources, please see the Academic Advising Resource List (\url{https://www.uaf.edu/advising/lr/SKM_364e19011717281.pdf})
\end{itemize}

\noindent{\bf Student Resources:}
\begin{itemize}
\setlength\itemsep{0em}
\item Disability Services (907-474-5655, \mailto{uaf-disability-services@alaska.edu}, Whitaker 208)
\item Student Health \& Counseling [6 free counseling sessions] (907-474-7043, \url{https://www.uaf.edu/chc/appointments.php}, Whitaker 203)
\item Center for Student Rights and Responsibilities (907-474-7317, \mailto{uaf-studentrights@alaska.edu}, Eielson 110)
\item Associated Students of the University of Alaska Fairbanks (ASUAF) or ASUAF Student Government (907-474-7355, \mailto{asuaf.office@alaska.edu}{asuaf.office@alaska.edu}, Wood Center 119)
\end{itemize}

\noindent{\bf Nondiscrimination statement:}
The University of Alaska is an affirmative action/equal opportunity employer and educational institution. The University of Alaska does not discriminate on the basis of race, religion, color, national origin, citizenship, age, sex, physical or mental disability, status as a protected veteran, marital status, changes in marital status, pregnancy, childbirth or related medical conditions, parenthood, sexual orientation, gender identity, political affiliation or belief, genetic information, or other legally protected status. The University's commitment to nondiscrimination, including against sex discrimination, applies to students, employees, and applicants for admission and employment. Contact information, applicable laws, and complaint procedures are included on UA's statement of nondiscrimination available at www.alaska.edu/nondiscrimination. For more information, contact:

\begin{tabular}{l}
UAF Department of Equity and Compliance\\
1760 Tanana Loop, 355 Duckering Building, Fairbanks, AK  99775\\
907-474-7300\\
\mailto{uaf-deo@alaska.edu}
\end{tabular}

 \scriptsize syllabus version: \today \normalsize

\end{document}

