\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}
\pagestyle{fancy} 
\lfoot{UAF Calculus 1}
\rfoot{first day }

\begin{document}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
\vspace*{-0.7in}
\begin{center}
  \large \sc{First Day of Class}
\end{center}


\begin{enumerate}
\item My teacher's name: \underline{\hspace{2in}}\\ 

office:  \underline{\hspace{2in}}\\ 

email:  \underline{\hspace{2in}}\\

My teacher's name: { Leah Berman or Jill Faudree or James Gossell}\\ office:  (Leah) Chap 102, {(Jill) Chap 306B, (James) Chap 301C}\\ email: {Leah lwberman@alaska.edu, (Jill) jrfaudree@alaska.edu, (James) jegossell@alaska.edu}\\

\item Where can I get information about this class?
\begin{itemize}
\item by attending class
\item from the course webpage: \textit{https://uaf-math251.github.io/} \\(or just google: Calculus I at UAF)
\item from Canvas
\end{itemize}

\vfill
\item Where is my textbook?
\begin{itemize}
\item Our text -- OpenStax Calculus Volume 1, authors Herman \& Strang -- is available free online. \\
(google \emph{openstax calculus I})
\item general info can be found here: \textit{https://openstax.org/details/books/calculus-volume-1} 
\item Note that it is possible to buy a hard copy. 
\item There are student resources online including a free student solutions manual.
\end{itemize}
\vfill
\item How will I know what will be happening each day in class?\\
On the webpage is a day by day schedule. It tells you what is happening in class every day. It gives the dates of all assessments including homework due dates, midterm dates, etc. 
\vfill
\item How will I my grade be determined in this course? \\
Based on class participation, homework completion, quizzes and their corrections, and some tests. Quizzes and tests are given in class.
\vfill
\item Is there any extra credit in this class or any free points?\\
Yes. \\
\begin{itemize}
	\item Free points for attending and participating in class. (All students should get 100\%!)
	\item Free point for turning in your homework. (All students should get 100\%!)
	\item Get 50\% of points back (aka extra credit) for correcting your quiz.
	\item Typically, midterms have extra credit problems that are designed to be just regular problems not extra hard problems.
\end{itemize}
Start earning those free points today!
\vfill
\item What do I need to do \textbf{this week} for this class?
\begin{itemize}
\item Attend class every day. 
\item Work all the problems from Chapter 1 Review. Ask questions! Turn them in by Thursday August 29. 
\item Sign up for a 2 hour time-slot to take your proctored ALEKS PPL no later than Friday August 30.
\end{itemize}
\vfill

\item What should I do if I miss class?\\
Contact your instructor and let them know if the absence is excused.\\
Make time to learn the material of the day you missed by 
\begin{enumerate}
	\item reading the book and/or watching a video
	\item working the problems on the sheet of the day
	\item start working the homework problems from the section
\end{enumerate}
\vfill

\item What should I do if I miss class on a quiz/midterm/final exam day?\\
Contact your instructor by email immediately. Explain why you missed class. Include the soonest available time you could make up the assessment if that is possible.
\vfill

\item Is the homework completed in an online system or do I write it down? Where do I find the homework problems? How do I turn in the homework?
\begin{itemize}
	\item You write your \textbf{solutions} (not just answers!!) on your paper or a tablet. 
	\item The problems can be found at the Course Webpage under the Homework tab. 
	\item You turn your work in electronically using Gradescope which you access from Canvas.
\end{itemize}
\vfill
\item Will I have answers or solutions to the homework? If so, where do I find them?\\
Yes. Complete solutions are on Canvas. Look in the \emph{Assessments} tab.
\vfill
\item Can I just copy the solutions, upload them to Canvas and get full credit? \\
Yes. \\
It should be clear that this is a very bad long-term strategy. 
\vfill
\item Can I see my grades?\\
Grades live in Canvas.
\vfill

\item What is the best way to get my questions answered?\\
It depends on the type of question but there several options:
\begin{itemize}
	\item in class
	\item depending on your instructor's schedule, just before and/or just after class
	\item in your teacher's office hour
	\item by appointment with your teacher
	\item by emailing your teacher
	\item in other teachers' and TA's tutoring/office hours
	\item in the Student Success Center
	\item using the 1-on-1 tutoring service
\end{itemize}

\vfill

\item Where can I get tutoring help?\\
In addition to getting help from your teacher, DMS has a special Math \& Stat help lab in the Student Success Center on the 6th floor of Rasmuson Library. This space is available for drop-in tutoring. We also offer one-on-one and online tutoring. For more information, google \textbf{Math Services University of Alaska Fairbanks} or check the link in the course webpage.\\

\item How will my teacher contact me? \\
In class, a Canvas announcement, or a Canvas email.\\

\item List the names of three people sitting next to you and give your name to them.\\

\item What are the habits \emph{you} would like to adopt this semester in this class?\\
Some ideas include:
\begin{itemize}
	\item Make it my default habit to be present in class every day.
	\item Work at least three homework problems from a section the same day the topic is covered in class.
	\item Circle homework problems I don't understand and ask about them, to my instructor or in the Math Lab.
	\item Form a study group to work on the homework by Week 2.
	\item When I work a homework problem, imagine I am explaining how to do it to someone else.
	\item Work a practice quiz/proficiency/midterm/final and then check my answers at least 24. hours before the real one.
\end{itemize}
\vfill
\end{enumerate}
\end{document}